---
title: "movie_rating"
author: "Tyler Brown"
date: "`r Sys.Date()`"
output: html_document
---

Choose six recent popular movies. Ask at least five people that you know (friends, family, classmates, imaginary
friends if necessary) to rate each of these movies that they have seen on a scale of 1 to 5. Take the results
(observations) and store them in a SQL database of your choosing. Load the information from the SQL database
into an R dataframe.

Install required packages.
```{r}
install.packages("RMySQL", dependencies = TRUE)
```
Attach the library to the environment.
```{r}
library(RMySQL)
```

Establish connection to the database.
```{r}
db <- dbConnect(MySQL(), user="root", password="", dbname="movie_rating", host="localhost", port=3306)
```

Establish connection to the database.
```{r}
query = paste0("SELECT * FROM movie_rating.movie_rating")
runQuerry = dbSendQuery(db, query)
df = fetch(runQuerry, n= -1)
```

Lets ensure the data was retrieved from the database.
```{r}
head(df)
```

I would like to edit the first friend's name to "Ash".
```{r}
df[df == '﻿Ash'] = 'Ash'
head(df)
```

Lets find the average rating of each friend. All "NA" values will be ignored.
```{r}
friend_mean = data.frame(Friend=df[,1], Mean=rowMeans(df[,-1], na.rm = TRUE))
friend_mean
```

Now lets add the "mean" to the dataframe as its own column.
```{r}
df$row_mean = rowMeans(df[,-1], na.rm = TRUE)
head(df)
```

If I include the column means, we can determine the average rating per movie and the average rating each friend made for each movie. Using this information, we can determine the popularity among the limited participants.
```{r}
colMeans(df[,-1], na.rm = TRUE)
```

