---
title: "Assignment5 Tidy and Transform"
author: "Tyler Brown"
date: "`r Sys.Date()`"
output: html_document
---

## Import Libraries
```{r}
library(tidyr)
library(dplyr)
```

## Read the Data
```{r}
url = 'https://raw.githubusercontent.com/AlphaCurse/DATA607/main/flights.csv'
df = read.csv(url)
head(df)
```

## Tidy and Transform Data
```{r}
colnames(df)[1] = 'Airline'
colnames(df)[2] = 'Status'
colnames(df)[3] = 'Los_Angeles'
colnames(df)[5] = 'San_Diego'
colnames(df)[6] = 'San_Francisco'
df = df %>%
  filter(!row_number() %in% c(3))
```

## Analysis comparing arrival delays

You can also embed plots, for example:

```{r}
df = df %>%
  mutate(Total = select(., Los_Angeles, Pheonix, San_Diego, San_Francisco, Seattle) %>% rowSums(na.rm = TRUE))
head(df)
```
Below, I have calculated the probability of a flight being delayed per airline. As we can see, Alaska has a 13% probability to be delayed, which is worse than AM West's probability of 10%. Customers may prefer to fly with AM West as oppose to Alaska due to the delay probability.
```{r}
alaska = (501/(501+3274))*100
am_west = (787/(787+6438))*100
alaska
am_west
```